Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-16 paper/ijcai16.tex
paper: remove synthetic 2 figures, update the others.
paper: move figures to their own directory.
As requested by Andrea.

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=16em]{setmargin}
    \end{center}
    \caption{\label{fig:setmargin} Intuition.}
\end{figure}

@@

\begin{figure}[b]
    \centering
    \begin{tabular}{cccc}
        {\bf synthetic 2} & {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5}
        \\
        \includegraphics[width=12em]{figure_synthetic_2_uniform} &
        \includegraphics[width=12em]{figure_synthetic_3_uniform} &
        \includegraphics[width=12em]{figure_synthetic_4_uniform} &
        \includegraphics[width=12em]{figure_synthetic_5_uniform}
        \\
        \includegraphics[width=12em]{figure_synthetic_2_uniform_sparse} &
        \includegraphics[width=12em]{figure_synthetic_3_uniform_sparse} &
        \includegraphics[width=12em]{figure_synthetic_4_uniform_sparse} &
        \includegraphics[width=12em]{figure_synthetic_5_uniform_sparse}
        \\
        \includegraphics[width=12em]{figure_synthetic_2_normal} &
        \includegraphics[width=12em]{figure_synthetic_3_normal} &
        \includegraphics[width=12em]{figure_synthetic_4_normal} &
        \includegraphics[width=12em]{figure_synthetic_5_normal}
        \\
        \includegraphics[width=12em]{figure_synthetic_2_normal_sparse} &
        \includegraphics[width=12em]{figure_synthetic_3_normal_sparse} &
        \includegraphics[width=12em]{figure_synthetic_4_normal_sparse} &
        \includegraphics[width=12em]{figure_synthetic_5_normal_sparse}
    \end{tabular}
    \caption{Results on the synthetic dataset. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: blue means $k=2$, greed $k=3$, and red $k=4$.}
\end{figure}

>>>>

\begin{figure}[t]
    \begin{center}
        \includegraphics[width=16em]{figures/setmargin}
    \end{center}
    \caption{\label{fig:setmargin} Intuition.}
\end{figure}

@@

\begin{figure}[b]
    \centering
    \begin{tabular}{ccc}
        {\bf synthetic 3} & {\bf synthetic 4} & {\bf synthetic 5}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_uniform_sparse} &
        \includegraphics[width=12em]{figures/synthetic_4_uniform_sparse} &
        \includegraphics[width=12em]{figures/synthetic_5_uniform_sparse}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal} &
        \includegraphics[width=12em]{figures/synthetic_4_normal} &
        \includegraphics[width=12em]{figures/synthetic_5_normal}
        \\
        \includegraphics[width=12em]{figures/synthetic_3_normal_sparse} &
        \includegraphics[width=12em]{figures/synthetic_4_normal_sparse} &
        \includegraphics[width=12em]{figures/synthetic_5_normal_sparse}
    \end{tabular}
    \caption{Results on the synthetic dataset. Each row represents a different
    setting: uniform, uniform sparse, normal, normal sparse. Color indicates
    the set size $k$: blue means $k=2$, greed $k=3$, and red $k=4$.}
\end{figure}
